Manuscript Figures

### 2021-09-29 src/manuscript_figures.Rmd
use parameters to pass experiment-related settings/projdir files as parameters. use R script to compile

---
title: "Manuscript Figures"
output:
  word_document: default
  html_document: default
params:
  settings_file: ''
  figures_folder: '/data/bimsbstatic/public/akalin/buyar/manuscript_figures_arcas/test'
  workdir: '.'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE, warning = FALSE, message = FALSE, 
                      fig.width = 9, fig.height = 11)
knitr::opts_knit$set(root.dir = params$workdir)
settings <- yaml::read_yaml(params$settings_file)
message(settings$GDCdataDir)
FigureFolder <- params$figures_folder
source(settings$utility_script)
library(data.table)
library(ggplot2)
library(pbapply)
library(ggrepel)
library(ggpubr)
library(cowplot)
library(ggridges)
library(ggcorrplot)
library(ComplexHeatmap)
library(pheatmap)
library(survminer)
library(survival)
library(caret)
library(treeheatr)
library(partykit)
theme_set(ggpubr::theme_pubclean())

geneSetScoresFolder <- '/data/local/buyar/arcas/subtyping_paper/data/geneset_scores/singscore'

inputDir <- settings$pipeline_output
assay_dir <- settings$assay_output$folder
surv <- do.call(rbind, readRDS(settings$surv))
projectDict <- sapply(yaml::read_yaml(settings$projectDict), 
                      function(x) gsub(' ', '', unlist(strsplit(x, ','))))
tcga_subtypes <- process_tcga_subtypes()

@@

```{r immunotherapy_response}
# immunotherapy response prediction analysis: 
# TODO: pass paths via args
projDir <- '/data/local/buyar/arcas/pancancer_multiomics_manuscript/results/immunotherapy_response/Mariathasan_et_al'
settings_imtrp <- yaml::read_yaml(file.path(projDir, 'settings.yaml'))
gex_all <- readRDS(file.path(projDir, 'mariathasan.gex.all_genes.normalised.RDS'))
human_gene_signatures <- readRDS(file.path(projDir, 'human_gene_signatures.RDS'))

LFs_imtrp <- import_LFs(c('maui_factors', 'mofa_factors', 'pca_factors'), settings_imtrp$pipeline_output)
FWs_imtrp <- import_feature_weights(c('maui_factors'), settings_imtrp$pipeline_output)
colData <- data.table::fread(settings_imtrp$clin)
colnames(colData)[1] <- 'bcr_patient_barcode'

@@

```{r tmz_gbm}
# TMZ resistance in GBM anaysis by Jona.
# Here I import figure data to have consistent figure styles
folder <- '/data/local/buyar/arcas/pancancer_multiomics_manuscript/results/tmz_gbm_jona'

>>>>

---
title: "Manuscript Figures"
output:
  word_document: default
  html_document: default
params:
  settings_file: 'settings.yaml' # settings file for pancancer analysis
  immther_projdir: 'immunotherapy_analysis' # settings file for immunotherapy analysis 
  tmz_gbm_figure_data_folder: 'data/tmz_gbm_figure_data' # path to data folder for tmz-gbm analysis 
  figures_folder: 'figures' 
  workdir: '.'
---

```{r knitr_setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE, warning = FALSE, message = FALSE, 
                      fig.width = 9, fig.height = 11, eval = TRUE)
knitr::opts_knit$set(root.dir = params$workdir)
```

```{r setup}
settings <- yaml::read_yaml(params$settings_file)
FigureFolder <- params$figures_folder
source(settings$utility_script)
library(data.table)
library(ggplot2)
library(pbapply)
library(ggrepel)
library(ggpubr)
library(cowplot)
library(ggridges)
library(ggcorrplot)
library(ComplexHeatmap)
library(pheatmap)
library(survminer)
library(survival)
library(caret)
library(treeheatr)
library(partykit)
theme_set(ggpubr::theme_pubclean())
inputDir <- settings$pipeline_output
assay_dir <- settings$assay_output$folder
surv <- do.call(rbind, readRDS(settings$surv))
projectDict <- sapply(yaml::read_yaml(settings$projectDict), 
                      function(x) gsub(' ', '', unlist(strsplit(x, ','))))

tcga_subtypes <- process_tcga_subtypes()

@@

```{r immunotherapy_response}
# immunotherapy response prediction analysis: 
projDir <- params$immther_projdir 
settings_imtrp <- yaml::read_yaml(file.path(projDir, 'settings_immther.yaml'))
gex_all <- readRDS(file.path(projDir, 'data', 'mariathasan.gex.all_genes.normalised.RDS'))
human_gene_signatures <- readRDS(file.path(projDir, 'data', 'human_gene_signatures.RDS'))

LFs_imtrp <- import_LFs(c('maui_factors', 'mofa_factors', 'pca_factors'), 
                        file.path(projDir, 'output'))
FWs_imtrp <- import_feature_weights(c('maui_factors'), file.path(projDir, 'output'))
colData <- data.table::fread(file.path(projDir, 'data', 'mariathasan.colData.csv'))
colnames(colData)[1] <- 'bcr_patient_barcode'

@@

```{r tmz_gbm}
# TMZ resistance in GBM anaysis by Jona.
# Here I import figure data to have consistent figure styles
folder <- params$tmz_gbm_figure_data_folder
